\documentclass[acmlarge,screen=true,anonymous=false,11pt]{acmart}

% ======================================================== 
%          Copyright & Conference setting
% ======================================================== 
% copyright
\setcopyright{none}
\settopmatter{printacmref=false, printccs=false, printfolios=true}

%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\usepackage{afterpage}
\usepackage{pdflscape}
\usepackage{pdfpages}

\usepackage{cleveref}
\crefname{mytheorem}{Theorem}{Theorems}

\usepackage{pgfplots}
\usepackage{textgreek}
\usepgfplotslibrary{groupplots}
\usetikzlibrary{patterns}

% ==== defined colors
\definecolor{myorange}{RGB}{244,106,18} %F47012
\definecolor{myblue}{RGB}{0,111,190}    %006FBE
\definecolor{mygreen}{RGB}{0,127,128}   %007F80
\definecolor{myred}{RGB}{228,46,36}     %E42E24
\definecolor{myyellow}{RGB}{198,148,34} %C69422
\definecolor{mydark}{RGB}{114,44,114}   %722C72
\definecolor{mymiddle}{RGB}{144,44,144} %902C90
\definecolor{mylight}{RGB}{167,44,167}  %A72CA7

\definecolor{light-cayenne}{RGB}{177,0,28} %B1001C
\definecolor{light-mocha}{RGB}{179,68,0}   %B34400
\definecolor{ocean}{RGB}{0,55,118}         %003776

\iffalse
\newtoggle{screen}
\toggletrue{screen}
\AtEndPreamble{%
\iftoggle{screen}
{
    \hypersetup{colorlinks, % 01/2018 Bei: change link colors all to blue
        linkcolor=blue,
        citecolor=blue,
        urlcolor=blue,
        filecolor=blue}
}
{
    \hypersetup{hidelinks}
}}
\fi

\begin{document}
\title{CENG 4120 Assignment 1}
\subtitle{Computer-Aided Design for Very Large Scale Integrated Circuits \\ Due Date: February 18 (Monday) 5:00pm}

\maketitle

\section{Library Analysis}
\href{https://www.eda.ncsu.edu/wiki/FreePDK45:Contents}{FreePDK 45nm Standard Cell Libaray} is used in this homework.
Open a terminal in a Department machine and upload \texttt{19hw1-src.zip}.
Extract the file with command \texttt{unzip 19hw1-src.zip}.
Open liberty file \texttt{gscl45nm.lib} in the directory with a text editor.
\begin{enumerate}
    \item Find cell \texttt{INVX1}. \begin{enumerate}
        \item What is the cell area?
        \item What is the function of pin \texttt{Y}?
    \end{enumerate}
    \item Find cell \texttt{FAX1}. \begin{enumerate}
        \item What is the cell area?
        \item What is the function of pin \texttt{YC}?
    \end{enumerate}
    \item Find cell \texttt{DFFPOSX1}. \begin{enumerate}
        \item What is the cell area?
        \item What is the cell leakage power?
    \end{enumerate}
\end{enumerate}

\section{Synthesis}
Change to the \texttt{19hw1-src} directory. Run \texttt{source setup.sh} in the directory to setup the environment variables of Synopsys Design Compiler. Synthesis 2-Bit Carry Look Ahead Adder \texttt{cla2.v} with library \texttt{gscl45nm.db}.
\begin{enumerate}
    \item Draw a gate-level schematic of the synthesized net-list.
    \item What is the total cell area?
    \item What is the total power consumption?
    \item Attach all scripts you used in file \texttt{cla2.tcl}.
\end{enumerate}

\section{Timing Optimization}
Design a 4-Bit Full Adder with five parameters using Verilog: a 4-bit output summation \texttt{sum}, a 1-bit output carry-out \texttt{cout}, two 4-bit input operands \texttt{a} and \texttt{b}, a 1-bit input carry-in \texttt{cin}. Synthesis your designed adder.
\begin{enumerate}
    \item Attach your Verilog in file \texttt{cla4.v}.
    \item What is the total cell area?
    \item What is the total power consumption?
\end{enumerate}
Setup a timing constraint 0.28 ns from operand \texttt{a} to summation \texttt{sum} and synthesis again.

\begin{enumerate}
    \setcounter{enumi}{3}
    \item What is the total cell area?
    \item What is the total power consumption?
    \item What is the slack?
    \item Attach all scripts you used in file \texttt{cla4.tcl}.
\end{enumerate}


\end{document}
